%!TEX program = pdflatex
\documentclass[11pt]{article}

% # FONTS

\usepackage[T1]{fontenc}
\renewcommand*\ttdefault{lmvtt}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{amsmath}
\usepackage[scaled=0.92]{PTSans}
\newcommand{\myul}[2][black]{\setulcolor{#1}\ul{#2}\setulcolor{black}}


% # GEOMETRY

\usepackage[
  paper  = letterpaper,
  left   = 1.0in,
  right  = 1.0in,
  top    = 1.0in,
  bottom = 1.0in,
]{geometry}
\usepackage[final,expansion=alltext]{microtype}
\usepackage[english]{babel}
\usepackage[parfill]{parskip}
\usepackage{afterpage}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{pifont}     % needed for dingbats for colophon
\usepackage{hyperref}

% # COLOR

\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{shadecolor}{gray}{0.9}

% # HEADERS

\usepackage{fancyhdr}
\fancyhf{}
\pagestyle{fancy}
\lhead{\textcolor{gray}{\emph{Evan Casey}}}
\rhead{\textcolor{gray}{\thepage}}
\renewcommand{\headrulewidth}{0pt}

% Renew section
\renewcommand{\section}[1]
{\vspace{1.0\baselineskip}{\Large\textbf{#1}}}

% Generate colophon at the end of the document
\newcommand{\makecolophon}
{\centering\ding{118} Last modified on \today~\ding{118}}

% Indent
\def\D{\par\noindent\makebox[1em][l]{-- }\hangindent1em}

\begin{document}
\thispagestyle{empty}

\parbox[c][0.5in]{3.4in}{\huge \textbf{Evan Casey}}
\parbox[c][0.5in]{2.5in}{%
\small
\vspace{17ex}
\texttt{evcasey.com} \\
\texttt{github.com/evancasey}
}

ML and Deep Learning Researcher \\
New York, NY 

\section{Experience}

\begin{itemize}[leftmargin=12pt]
 \item[] \textbf{Consultant} -- AI Reverie \hfill August 2018 - Present
   \begin{enumerate}[leftmargin=2em,labelindent=16pt,label=$\bullet$]
      \item Researching and building systems for improving computer vision with synthetic data, transfer learning, and domain adaptation (both pixel-level and model-level).
    \end{enumerate}
  \item[] \textbf{Research Engineer} -- Cogitai \hfill May 2017 - July 2018
    \begin{enumerate}[leftmargin=2em,labelindent=16pt,label=$\bullet$]
      \item Research software engineer on the robotics team working on self-supervising systems for visual perception and manipulation under the supervision of Satinder Singh and Peter Stone.
      \item Developed large sections of Cogitai's machine learning and robotics libraries. Implemented, and productionized various RL algorithms (A2C, PPO, DQN, SAC) within a large scale learning system.
      \item Led the engineering effort on an action-conditional world model that learns from unlabeled sensory experiences. Used the learned features to perform diverse tasks on physical robots.
    \end{enumerate}
  \item[] \textbf{Sabbatical} -- Recurse Center \hfill March 2016 - June 2016
    \begin{enumerate}[leftmargin=2em,labelindent=16pt,label=$\bullet$]
      \item 3-month sabbatical of self-directed research in deep learning and reinforcement learning. Read lots of papers, implemented some of them.
    \end{enumerate}
  \item[] \textbf{Date Engineer} -- Tapad (acquired by Telenor in Feb. 2016) \hfill May 2014 - March 2016 
    \begin{enumerate}[leftmargin=2em,labelindent=16pt,label=$\bullet$]
      \item Built and maintained large-scale (100TB+) Hadoop pipelines powering a graph-based representation of device ownership that uses a probabilistic model to infer relationships.
      \item Led development of Tapad's ad inventory forecasting system, which ingests billion of records daily in Elasticsearch. Researched and implemented algorithms for large-scale audience clustering.
      \item Backend development on a realtime ad buying platform. Low latency (95th percentile response time around 25ms), high throughput (peaking above 750k QPS).
    \end{enumerate}
  \item[] \textbf{Engineering Intern} -- One Kings Lane \hfill Summer 2013 
    \begin{enumerate}[leftmargin=2em,labelindent=16pt,label=$\bullet$]
      \item Built a product recommendation service based on multi-armed bandits and contributed to Babar, an A/B testing framework using Ruby on Rails.
    \end{enumerate}
\end{itemize}

\section{Publications}

\textsc{Conference Papers}
\begin{itemize}[leftmargin=12pt]
  \item[] Thinking Between the Lines: Guided 2D Animation with Generative Adversarial Networks \hfill 2018 \\
  \textbf{Evan Casey}, Harry Teitelman \\
  Accepted as Poster at NIPS Workshop on Machine Learning for Creativity and Design
\end{itemize}

\textsc{Undergraduate Thesis}
\begin{itemize}[leftmargin=12pt]
  \item[] Scalable Collaborative Filtering Recommendation Algorithms on Apache Spark \hfill 2014 \\
  \textbf{Evan Casey}, Deanna Needell \\
  Outstanding Thesis in Mathematics and Computer Science
    
\end{itemize}


\section{Teaching and Talks}
\begin{itemize}[leftmargin=12pt]
  \item[] Workshop | AI Atelier
  \hfill June 2018
  \\ Applied Deep Learning with Tensorflow 
  \item[] Workshop | AI Atelier
  \hfill May 2018
  \\ Applied Deep Learning with Tensorflow
  \item[] Talk | New York Times Research
  \hfill November 2016
  \\  Deep Reinforcement Learning with Policy Optimization
  \item[] Workshop | Recurse Center
  \hfill June 2016 
  \\ Introduction to Neural Networks with Tensorflow
  \item[] Talk | HackNY Masters Series
  \hfill October 2015
  \\ Scalable Machine Learning with Apache Spark
  \item[] Teaching Assistant | Claremont McKenna College
  \hfill Spring 2012
  \\ MATH 152: Statistical Inference
\end{itemize}

\section{Education}

\begin{itemize}[leftmargin=12pt]
  \item[] B.A. Mathematics, Economics, minor in Computer Science \\
    \textbf{Claremont McKenna College}\hfill 2010--2014 
    \begin{enumerate}[leftmargin=2em,labelindent=16pt,label=$\bullet$]
      \item Selected coursework: Machine Learning, Real Analysis, Complex Analysis, Probability Theory, Statistical Inference, Differential Equations, Discrete Mathematics, Data Structures \& Algorithms
    \end{enumerate}
\end{itemize}

\section{Achievements}

\begin{itemize}[leftmargin=12pt]
  \item[] HackNY Fellowship -- Summer internship program
  \hfill 2014
  \item[] Finalist -- Greylock Hackfest 
  \hfill 2013
  \item[] Janet Myhre \& Leon Hollerman Scholarship
  \hfill 2010 - 2014
\end{itemize}


%\section{Popular Press}
%\section{Awarded Grants}

%\section{Industry}

\section{Other}

Outside of machine learning research, I am a skateboarder and visual artist. In high school, I raised \$875,000 in grant money for a skate park in my hometown and once lived in Mongolia for a summer.

%\textsc{Senior Program Committee}
%\textsc{Associate Editor and Editorial Board}


%\textsc{Grant Reviewing}
%\textsc{Former Ph.D. Students}
%\textsc{Current Ph.D. Students}
%\textsc{Postdoctoral Fellows}
%\textsc{Other Ph.D. Thesis Committees}
%\textsc{Mentoring}
%\textsc{Advising and Consulting}


%\vfill
%\makecolophon

\end{document}

